<!--
%\VignetteEngine{knitr}
%\VignetteIndexEntry{Example using equations and figures}
-->

An Example vignette with demonstrations
=======================================


```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(out.extra='style="display:block; margin: auto"'
    #, fig.align="center"
    , fig.width=4.3, fig.height=3.2, dev.args=list(pointsize=10)
    )
knit_hooks$set(spar = function(before, options, envir) {
    if (before){
        par( las=1 )                   #also y axis labels horizontal
        par(mar=c(2.0,3.3,0,0)+0.3 )  #margins
        par(tck=0.02 )                          #axe-tick length inside plots             
        par(mgp=c(1.1,0.2,0) )  #positioning of axis title, axis labels, axis
     }
})
```


Introduction
------------

TODO Some general explantion of the task and setup that hte package addresses.

Example data
------------

```{r}
packageDir <- system.file(package='FieldSpectroscopyCC')	# only works if package has been installed
dataDir <- file.path(packageDir,"data")
load(file.path(dataDir,"outdoor_rad_cal_data.Rdata"))
load(file.path(dataDir,"atmospheric_absorption_regions.Rdata"))
integration_time<-450
str( outdoor_rad_cal_data, max.level = 1 )
```

TODO explain the example data.

TODO shorten name of dataset, to shorten code samples. 

TODO use more descriptive names inside the dataset.

Processing
----------
First, the raw measurement need to be devided by integration time, 
and several spectra are summarized to a mean spectrum.
```{r}
DN_mat<-DN_spectral_matrix_for_rad_cal(outdoor_rad_cal_data$DN_matrix,integration_time=integration_time)
radiance_mean<-StatsOnSpectra(wl=outdoor_rad_cal_data$radiance_wl,spectra=outdoor_rad_cal_data$radiance_matrix,fun='mean')
str(radiance_mean)
```

For the calibration, the spectrum needs to be available at given reference wavelength, 
which are linearly interpolated from the mean spectrum.

TODO: What is $wp_coef?

```{r}
radiance_mean_res<-linear_resample(outdoor_rad_cal_data$radiance_wl,radiance_mean,outdoor_rad_cal_data$DN_wl)
wp_coeff_res<-linear_resample(outdoor_rad_cal_data$wp_coef$V1,outdoor_rad_cal_data$wp_coef$V2,outdoor_rad_cal_data$DN_wl)
DN_mat<-DN_spectral_matrix_for_rad_cal(outdoor_rad_cal_data$DN_matrix,integration_time=integration_time)
radiance_mean<-StatsOnSpectra(wl=outdoor_rad_cal_data$radiance_wl,spectra=outdoor_rad_cal_data$radiance_matrix,fun='mean')
str(radiance_mean)
```

TODO explain the other things
Thomas did not understand it fully yet, what is radiance compared to DN?
 
```{r}
#calculate mean of several spectra
DN_mean<-StatsOnSpectra(wl=outdoor_rad_cal_data$DN_wl,spectra=outdoor_rad_cal_data$DN_matrix,fun='mean')
#calculate calibration coefficients
rad_cal<-radiometric_calibration(type=1,wl=outdoor_rad_cal_data$DN_wl,radiance_mean_res,DN_mean)
#exclude regions of the spectrum affected by atmospheric absorptions and noisy pixels
range_to_exclude<-data.frame(wl_start=c(outdoor_rad_cal_data$DN_wl[1],outdoor_rad_cal_data$DN_wl[length(outdoor_rad_cal_data$DN_wl)-35]),wl_end=c(outdoor_rad_cal_data$DN_wl[30],outdoor_rad_cal_data$DN_wl[length(outdoor_rad_cal_data$DN_wl)]))
atmospheric_absorption_regions<-rbind(atmospheric_absorption_regions,c(range_to_exclude))
exclude_atmospheric_absorption_features<-exclude_spectral_regions(wl=outdoor_rad_cal_data$DN_wl,rad_cal,atmospheric_absorption_regions)
#smooth results
rad_cal_coeff<-spline_smooth_gapfilling(wl=outdoor_rad_cal_data$DN_wl,exclude_atmospheric_absorption_features) 
```

```{r ci, spar=TRUE}
plot(outdoor_rad_cal_data$DN_wl,rad_cal,ylim=c(0,0.000025))
points(outdoor_rad_cal_data$DN_wl,exclude_atmospheric_absorption_features,pch=20,col="red")
lines(outdoor_rad_cal_data$DN_wl,rad_cal_coeff,col="green",lwd=2)
lines(outdoor_rad_cal_data$DN_wl,rad_cal_edge_coef,col="dark green",lwd=2)
```


